\large{\bf Looking forwards and backwards: dynamics and genealogies of locally regulated populations }

### 2023-05-01 forwards-and-backwards.tex
minor edits

Since we take bounded $f$,
for most situations the bound $C_f(1+|f(x)|)$ in condition~\ref{gamma_B_condition} above
can be safely replaced simply by $C_f$;
however, this will be useful
in certain situations where we consider a sequence of $f$ with increasing upper bounds.
We now give two concrete situations in which condition~\ref{gamma_B_condition} is satisfied.

@@

Recall when interpreting~\eqref{eqn:limiting_mgale_problem}
that, for instance, $r(x, \eta_s) = r(x, \smooth{r} \eta_s(x))$,
and so $\DG(fr)(x) = \DG(f(\cdot) r(\cdot, \smooth{r} \eta_s(\cdot)))(x)$.

@@

\paragraph{Two-step convergence to PDE:}
Although the coefficients at $x$ in \eqref{eqn:nonlocal_pde} are nonlocal,
we can choose our kernels $\rho_\gamma$, $\rho_r$, and $\rho_F$
in such a way that they depend only on the population in a region close to $x$,
and so we expect that under rather general conditions
solutions of the nonlocal PDE will be close to the corresponding 
classical PDE.
The following propositions provide two concrete situations in which this is true.
In the first, the PDE is a reaction-diffusion equation, and we borrow
an idea from~\cite{penington:2017} to express the solutions to both the nonlocal
equation and the classical PDE through a Feynman-Kac formula.

@@

\begin{proposition}
	\label{nonlocalPME to PME}
Suppose that
we can write $\rho_\gamma=\zeta*\check{\zeta}$, where $\check{\zeta}(x)=\zeta(-x)$ and
$\zeta\in\mathcal{S}(\IR^d)$ (the Schwartz space of rapidly decreasing functions).
Furthermore, suppose that %$\psi_0^\epsilon\in L^1(\IR^d)$, 
$\psi_0^\epsilon\geq 0$ is such that
there exist $\lambda\in (0,1)$ and $C\in (0,\infty)$ (independent
of $\epsilon$) such that 
\begin{equation*}
\int\exp(\lambda \|x\|)\psi_0^\epsilon(x)dx<C,\quad\mbox{ and }
\sup_\epsilon\int \psi_0^\epsilon|\log \psi_0^\epsilon|dx<\infty,
\end{equation*}
with
$\psi_0^\epsilon\rightharpoonup \psi_0$ as $\epsilon\to 0$. Then
writing $\psi^\epsilon$ for the solution to~(\ref{mollified equation})
on $[0,T]\times \IR^d$ with
initial condition $\psi_0^\epsilon$,
$\psi^\epsilon\rightharpoonup \psi$ as $\epsilon\to 0$ where
$\psi\in L_t^2(H^1)\cap C_t(L^1)$, $\int \psi|\log \psi| dx<\infty$, and
$\psi$ solves~(\ref{PME}) on $[0,T]\times \IR^d$. 
\end{proposition}
The example that we have in mind for the kernel $\rho_\gamma$ is a Gaussian
kernel.
\begin{remark}
Although it seems hard to formulate an all-encompassing result,
Propositions~\ref{prop:nonlocal_to_local} and~\ref{nonlocalPME to PME} are by no
means exhaustive. When the scaling limit is deterministic, one can 
expect analogous results under rather general conditions. However, when the limit
points are stochastic, they resemble ``nonlinear superprocesses'' and so one cannot
expect a density with respect to Lebesgue measure in $d\geq 2$. It is then not
reasonable to 
expect to be able to make sense of the limit if we scale the kernels in this way.
Moreover, in one dimension, where the classical superprocess does have a density with 
respect to Lebesgue measure, the form of~(\ref{eqn:limiting_mgale_problem})
suggests that even if one can remove the local averaging from $\gamma$, it
will be necessary
to retain averaging of $r$ in order to obtain a well-defined limit. 
\end{remark}

Proofs of the results so far, on nonlocal processes, are found in Section~\ref{sec:proofs}.

@@

\comment{FROM ALISON: should we signpost that the proofs of these results can 
be found in section???}

@@

\subsection{Preliminaries}

@@

% % % % % % % % % % % % %
\subsection{Proof of Theorem~\ref{thm:nonlocal_convergence}: limit points for the nonlocal process}
    \label{sec:population_density_proof}

@@

\subsubsection{Porous Medium Equation}

@@

In order to identify the limit point of any convergent subsequence
of $\{\rho_\epsilon*\eta^N(x)\}$, 
we are going to require some control on the spatial continuity of the 
functions $\rho_\epsilon*\eta^N(x)$. This will be inherited from the regularity
of the transition density of the 
Gaussian random walk with generator ${\cal L}^\theta$, which in turn follows
from its representation
as that of a Brownian motion evaluated at the random time $T(t)$ defined
in Lemma~\ref{PsiBoundHS}.
Our approach will be to 
approximate $\psi_t^{\epsilon,x}(\cdot)$ by $p_{\epsilon^2+t}(x, \cdot)$,
and to control the error that this introduces we 
need to control $T(t)-t$.

@@

    For the third term, we will first collect some facts.
    Observe that on the event $A_3$,
    $\epsilon^2 + t + \tau(t)$ is between
    $(\epsilon^2 + t)/ 2$ and $3(\epsilon^2 + t)$,
    and for any $s$ in this interval,
    \begin{align}
        p_{2s}(y)
        &\le \nonumber
        \left( \frac{
            2 (\epsilon^2 + t)3
        }{
            \epsilon^2 + t
        } \right)^{d/2}
        p_{6(\epsilon^2 + t)}(x, y)
        \\ &= \label{eqn:p_bounded_on_interval}
        6^{d/2}
        p_{6(\epsilon^2 + t)}(x, y) .
    \end{align}
    Moreover, since $u e^{-u} \le e^{-1}$ for all $u \ge 0$,
    \begin{align}
        \frac{\|x - y\|^2}{s} p_s(x, y)
        &= \nonumber
        \frac{4}{(2 \pi s)^{d/2}}
        e^{- \frac{ \|x-y\|^2 }{ 4s }}
        \frac{\|x-y\|^2}{4s}
        e^{- \frac{ \|x-y\|^2 }{ 4s }}
        \\ &\le \label{eqn:p_deriv_term2}
        C p_{2s}(x, y) .
    \end{align}
    Now, by the Intermediate Value Theorem,
    \begin{align}
\label{deduction from IVT}
        \left|
            p_{\epsilon^2 + t + \tau(t)}(x, y)
            -
            p_{\epsilon^2 + t}(x, y)
        \right|
        &=
        \left| \tau(t) \right|
        \left| \frac{\partial p_s(x, y)}{\partial s} \right|
    \end{align}
    for some $s$ between $\epsilon^2 + t + \tau(t)$ and $\epsilon^2 + t$.
   Since 
    \begin{align*}
        \partial_ s p_s(x, y)
        &=
        \partial_s
        \left(
            \frac{1}{(2 \pi s)^{d/2}}
            \exp\left( - \frac{\|x - y\|^2}{2 s} \right)
        \right)
        \\ &=
        - \frac{d}{2s} p_s(x, y) + \frac{\|x - y\|^2}{2 s^2} p_s(x, y),
    \end{align*}
    applying the inequality~\eqref{eqn:p_deriv_term2},
    using the fact that $p_s(x, y) \le 2^{d/2} p_{2s}(x,y)$,
    and then \eqref{eqn:p_bounded_on_interval},
    we have that for any $s \in ((\epsilon^2 + t)/ 2, 3(\epsilon^2 + t))$,
    \begin{align*}
        \left| \frac{\partial}{\partial s} p_s(x, y) \right|
        \le
        \frac{C}{s} p_{2s}(x, y) 
        \le
        \frac{C}{\epsilon^2 + t} p_{6(\epsilon^2 + t)}(x, y) .
    \end{align*}
    Therefore, recalling that $\IE[\tau(t)^2] = t / \theta$, substituting 
into~(\ref{deduction from IVT}),
    \begin{align*}
        \IE\left[
            1_{A_3}
            \left|
                p_{\epsilon^2 + t + \tau(t)}(x, y)
                -
                p_{\epsilon^2 + t}(x, y)
            \right|
        \right]
        &\le
            \frac{C}{\epsilon^2 + t}
                p_{6(\epsilon^2 + t)}(x, y)
            \IE\left[|\tau(t)|\right]
        \\ &\le
            \frac{C}{\epsilon^2 + t}
                p_{6(\epsilon^2 + t)}(x, y)
            \IE\left[\tau(t)^2\right]^{1/2}
        \\ &=
            \left( \frac{Ct}{\theta(\epsilon^2 + t)^2} \right)^{1/2}
                p_{6(\epsilon^2 + t)}(x, y)
        \\ &\le
            \frac{C}{\sqrt{\theta \epsilon^2}}
                p_{6(\epsilon^2 + t)}(x, y) ,
    \end{align*}
    where the last inequality follows from $2 \epsilon^2 t \le (\epsilon^2 + t)^2$.

@@

    Expanding the difference of two squares,
    \begin{align*}
        e^{- \frac{\|y-z\|^2}{2 s}}
        -
        e^{- \frac{\|x-z\|^2}{2 s}}
        &=
        \left(
            e^{-\frac{\|y-z\|^2}{4 s}}
            -
            e^{-\frac{\|x-z\|^2}{4 s}}
        \right)
        \left(
            e^{-\frac{\|y-z\|^2}{4 s}}
            +
            e^{-\frac{\|x-z\|^2}{4 s}}
        \right) .
    \end{align*}
Now, thinking of the first term in brackets as a function of a single variable on
the line segment $[y,z]$ connecting $y$ to $z$, we can apply the
Intermediate Value Theorem and take the modulus to bound this expression by 
    \[
        \|y-x\|
        \left( \frac{2\|w-z\|}{4s} \exp\left(-\frac{\|w-z\|^2}{4s}\right)\right)
        (4 \pi s)^{d/2}
        \left( p_{2s}(y,z)+p_{2s}(x,z) \right)
    \]
    for some $w\in [y,z]$.
    Using the fact that $x e^{-x^2}$ is uniformly bounded,
    we can bound the first bracket in the last equation by $C/\sqrt{s}$, and the result follows.
\end{proof}

@@

\big\langle |p_{s-r+\epsilon^2}(y,z)-p_{s-r+\epsilon^2}(w,z)| 

@@

	+ \big\langle\frac{C}{(\theta\epsilon^2)^{1/2}} \Big(%\big\langle 
	p_{6(\epsilon^2+s)}(y,z)+p_{6(\epsilon^2+s)}(w,z)\Big) %, \eta_0(dz)
%\big\rangle
	+\widehat{\epsilon}(\delta,\epsilon,\theta) %\langle 1

@@

\big(p_{2(s+\epsilon^2}(y,z)+p_{2(s+\epsilon^2}(w,z)\big),\eta_0(dz)\Big\rangle

@@

\big(p_{2(s-t+\epsilon^2}(y,z)+p_{2(s-r+\epsilon^2}(w,z)\big)

@@

@@

We now turn to the identification of the limit points of the sequence 
$\big\{\big(\rho_\epsilon*\eta_t^N(x)dx\big)_{t\geq 0}\big\}_{N\geq 1}$.
We would like to show that any limit point solves~\eqref{target equation in local convergence}
in the limit, i.e.,
\begin{equation}\label{eqn:target PDE weak form}
    \langle f(x), \varphi(t,x)dx \rangle
    =
    \int_0^t
        \Big\langle
        \frac{1}{2}\Delta f(x) + f(x) F(\varphi(s,x))
        ,
        \varphi(s,x) dx
        \Big\rangle
    ds .
\end{equation}
Since 
$\langle f, \rho_\epsilon*\eta_t^N(x)dx\rangle=
\langle \rho_\epsilon*f(x), \eta_t^N(dx)\rangle$,
this will follow if we can show that each the terms in the semimartingale
decomposition~(\ref{eqn:eta_martingale}),
with the test function $f$ replaced by $\rho_\epsilon*f(\cdot)$,
converges to the corresponding term in~\eqref{eqn:target PDE weak form}.

The linear term is straightforward.
Write $T_{\cdot}$ for the heat semigroup, so that
$\rho_\epsilon*f(x) = T_{\epsilon^2}f(x)$.
By a Taylor expansion, writing $\{T_t\}_{t\geq 0}$ for the heat semigroup,
\begin{align*}
\int_0^t \big\langle \mathcal{L}^\theta T_{\epsilon^2} f, 
	\eta_s^N(dx)\big\rangle ds 
&= \int_0^t \big\langle \frac{1}{2} \Delta T_{\epsilon^2} f(x), 
	\eta_s^N(dx) \big\rangle 
	+ \mathcal{O}\Big(\frac{1}{\theta}\Big) 
\\ &= \int_0^t \big\langle \frac{1}{2} \Delta f(x), \rho_\epsilon* \eta_s^N(x) dx 
	\big\rangle ds + \mathcal{O}\Big(\frac{1}{\theta}\Big).
\end{align*}
Thus, from weak convergence we can deduce that under our scaling,
for any (weakly) convergent subsequence $\{\rho_\epsilon*\eta^N(x)dx\}_{N\geq 1}$,
\[ 
\int_0^t \big\langle \mathcal{L}^\theta T_{\epsilon^2} f, 
\eta_s^N(dx)\big\rangle ds 
\rightarrow \int_0^t \big\langle \frac{1}{2} \Delta f(x), 
\varphi (s,x) dx \big\rangle ds. 
\]

@@

We first note that,
\begin{align*}
    &
\langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \eta_s(y)), 
\rho_\epsilon * \eta_s(y) dy \rangle 
-\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\eta_s(dy)), \eta_s(dy) \rangle 
\\ 
& = 
\langle \int T_{\epsilon^2} f(y) 
F(\rho_\epsilon * \eta_s(y))\rho_\epsilon(y-w) dy, \eta_s(dw)\rangle - \langle 
T_{\epsilon^2} f(w) F(\rho_\epsilon*\eta_s(w)), \eta_s(dw) \rangle 
\\ 
&= 
\langle \int \big\{ T_{\epsilon^2} f(y) F(\rho_\epsilon*\eta_s(y))-T_{\epsilon^2}f(w) 
F(\rho_\epsilon*\eta_s(w))\big\} 
\rho_\epsilon(w-y)dy, \eta_s(dw) \rangle.
\end{align*}
Let us denote the integral against $dy$ in the last expression by $I$, that is 
\[ I :=  \int \{ T_{\epsilon^2} f(y) 
F(\rho_\epsilon*\eta_s(y))-T_{\epsilon^2}f(w) 
F(\rho_\epsilon*\eta_s(w))\} \rho_\epsilon(w-y)dy, \]
and note that $|I|$ is bounded by
\begin{align}
& \int 
\Big\{ |F(\rho_\epsilon*\eta_s(y))-F(\rho_\epsilon*\eta_s(w))|T_{\epsilon^2}f(y)+
F(\rho_\epsilon*\eta_s(w))|T_{\epsilon^2}f(y)-T_{\epsilon^2}f(w))|\Big\} 
\rho_{\epsilon}(w-y)dy
\nonumber \\ &\leq \int \| f\|_{\infty} 
\big|F(\rho_\epsilon*\eta_s(y))-F(\rho_\epsilon*\eta_s(w))\big| \rho_\epsilon(w-y)dy + 
C \epsilon\|f' \|_\infty |F(\rho_\epsilon*\eta_s(w))|, \label{FirstBoundCT}
\end{align}
where we have used that 
\[
\int |T_{\epsilon^2}f(y)-T_{\epsilon^2}f(w)| p_{\epsilon^2}(w,y)dy
\leq \|f'\|_\infty\int|y-w|p_{\epsilon^2}(w,y)dy.
\]
Now recall that $F$ is a polynomial of degree $n$, and so 
there exist real numbers $b_k$ such
that $F(a)-F(b)= (a-b)\sum_{k=1}^{n-1}b_kx^ky^{n-1-k}$ and so 
\[
|F(\rho_\epsilon*\eta_s(y))-F(\rho_\epsilon*\eta_s(w))|
\leq 
|\rho_\epsilon*\eta_s(y)-\rho_\epsilon*\eta_s(w)|
\sum_{k=1}^{n-1}|b_k|\left(\rho_\epsilon*\eta_s(y)^{n-1}+\rho_\epsilon*\eta_s(w)^{n-1}\right).
\]

Combining the above, we have reduced the problem to showing that 
\begin{equation}
\label{target expression}
	\lim_{\epsilon\to 0}
	\IE\Big[	\int_0^t\big\langle \int |\rho_\epsilon*\eta_s(y)-\rho_\epsilon*\eta_s(w)|
\left(\rho_\epsilon*\eta_s(y))^k+\rho_\epsilon*\eta_s(w)^k\right)
	p_{\epsilon^2}(w,y)dy, \eta_s(dw)\big\rangle ds\Big]
=0,
\end{equation}
We are going to use the estimate~(\ref{difference in rhos}).
First note that by Lemma~\ref{bounds on moments}
the contribution to~(\ref{target expression}) from the integral over
the time interval $[0,\delta]$ is ${\mathcal O}(\delta)$. We focus instead
on the interval $(\delta, t]$.

>>>>

Since we take bounded $f$,
for most situations the bound $C_f(1+|f(x)|)$ in condition~\ref{gamma_B_condition} above
can be safely replaced simply by $C_f$;
however, this will be useful
in certain situations where we consider a sequence of $f$ with increasing upper bounds.
We now give two concrete situations in which condition~\ref{gamma_B_condition} is satisfied.
The proof is in Section~\ref{sec:preliminary_proofs}.

@@

Recall when interpreting~\eqref{eqn:limiting_mgale_problem}
that, for instance, $r(x, \eta_s) = r(x, \smooth{r} \eta_s(x))$,
and so $\DG(fr)(x) = \DG(f(\cdot) r(\cdot, \smooth{r} \eta_s(\cdot)))(x)$.
The proof of this theorem appears in Section~\ref{sec:population_density_proof}.

@@

\paragraph{Two-step convergence to PDE:}
Although the coefficients at $x$ in \eqref{eqn:nonlocal_pde} are nonlocal,
we can choose our kernels $\rho_\gamma$, $\rho_r$, and $\rho_F$
in such a way that they depend only on the population in a region close to $x$,
and so we expect that under rather general conditions
solutions of the nonlocal PDE will be close to the corresponding 
classical PDE.
The following propositions provide two concrete situations in which this is true.
In the first, the PDE is a reaction-diffusion equation, and
in the proof in Section~\ref{two-step convergence to FKPP} we borrow
an idea from~\cite{penington:2017} to express the solutions to both the nonlocal
equation and the classical PDE through a Feynman-Kac formula.

@@

\begin{proposition}
	\label{nonlocalPME to PME}
Suppose that
we can write $\rho_\gamma=\zeta*\check{\zeta}$, where $\check{\zeta}(x)=\zeta(-x)$ and
$\zeta\in\mathcal{S}(\IR^d)$ (the Schwartz space of rapidly decreasing functions).
Furthermore, suppose that %$\psi_0^\epsilon\in L^1(\IR^d)$, 
$\psi_0^\epsilon\geq 0$ is such that
there exist $\lambda\in (0,1)$ and $C\in (0,\infty)$ (independent
of $\epsilon$) such that 
\begin{equation*}
\int\exp(\lambda \|x\|)\psi_0^\epsilon(x)dx<C,\quad\mbox{ and }
\sup_\epsilon\int \psi_0^\epsilon|\log \psi_0^\epsilon|dx<\infty,
\end{equation*}
with
$\psi_0^\epsilon\rightharpoonup \psi_0$ as $\epsilon\to 0$. Then
writing $\psi^\epsilon$ for the solution to~(\ref{mollified equation})
on $[0,T]\times \IR^d$ with
initial condition $\psi_0^\epsilon$,
$\psi^\epsilon\rightharpoonup \psi$ as $\epsilon\to 0$ where
$\psi\in L_t^2(H^1)\cap C_t(L^1)$, $\int \psi|\log \psi| dx<\infty$, and
$\psi$ solves~(\ref{PME}) on $[0,T]\times \IR^d$. 
\end{proposition}
The example that we have in mind for the kernel $\rho_\gamma$ is a Gaussian kernel.
For the proof, see Section~\ref{sec:pme}.
\begin{remark}
Although it seems hard to formulate an all-encompassing result,
Propositions~\ref{prop:nonlocal_to_local} and~\ref{nonlocalPME to PME} are by no
means exhaustive. When the scaling limit is deterministic, one can 
expect analogous results under rather general conditions. However, when the limit
points are stochastic, they resemble ``nonlinear superprocesses'' and so one cannot
expect a density with respect to Lebesgue measure in $d\geq 2$. It is then not
reasonable to 
expect to be able to make sense of the limit if we scale the kernels in this way.
Moreover, in one dimension, where the classical superprocess does have a density with 
respect to Lebesgue measure, the form of~(\ref{eqn:limiting_mgale_problem})
suggests that even if one can remove the local averaging from $\gamma$, it
will be necessary
to retain averaging of $r$ in order to obtain a well-defined limit. 
\end{remark}

@@

Both results are proved in Section~\ref{sec:lookdown_proofs}.

@@

\subsection{Preliminaries}
\label{sec:preliminary_proofs}

@@

% % % % % % % % % % % % %
\subsection{Proof of Theorem~\ref{thm:nonlocal_convergence}: convergence for the nonlocal process}
    \label{sec:population_density_proof}

@@

\subsubsection{Porous Medium Equation}
\label{sec:pme}

@@

To identify the limit point of any convergent subsequence
of $\{\rho_\epsilon*\eta^N(x)\}$, 
we will require some control on the spatial continuity of the 
functions $\rho_\epsilon*\eta^N(x)$. This will be inherited from the regularity
of the transition density of the 
Gaussian random walk with generator ${\cal L}^\theta$, which in turn follows
from its representation
as that of a Brownian motion evaluated at the random time $T(t)$ defined
in Lemma~\ref{PsiBoundHS}.
Our approach will be to 
approximate $\psi_t^{\epsilon,x}(\cdot)$ by $p_{\epsilon^2+t}(x, \cdot)$,
and to control the error that this introduces we 
need to control $T(t)-t$.

@@

    For the third term, we will first collect some facts.
    Observe that on the event $A_3$,
    $\epsilon^2 + t + \tau(t)$ is between
    $(\epsilon^2 + t)/ 2$ and $3(\epsilon^2 + t)$,
    and for any $s$ in this interval,
    \begin{align}
        p_{2s}(y)
        &\le \nonumber
        \left( \frac{
            6 (\epsilon^2 + t)
        }{
            \epsilon^2 + t
        } \right)^{d/2}
        p_{6(\epsilon^2 + t)}(x, y)
        \\ &= \label{eqn:p_bounded_on_interval}
        6^{d/2}
        p_{6(\epsilon^2 + t)}(x, y) .
    \end{align}
    Moreover, since $u e^{-u} \le e^{-1}$ for all $u \ge 0$,
    \begin{align}
        \frac{\|x - y\|^2}{s} p_s(x, y)
        &= \nonumber
        \frac{4}{(2 \pi s)^{d/2}}
        e^{- \frac{ \|x-y\|^2 }{ 4s }}
        \frac{\|x-y\|^2}{4s}
        e^{- \frac{ \|x-y\|^2 }{ 4s }}
        \\ &\le \label{eqn:p_deriv_term2}
        C p_{2s}(x, y) .
    \end{align}
    Now, by the Intermediate Value Theorem,
    \begin{align}
\label{deduction from IVT}
        \left|
            p_{\epsilon^2 + t + \tau(t)}(x, y)
            -
            p_{\epsilon^2 + t}(x, y)
        \right|
        &=
        \left| \tau(t) \right|
        \left| \frac{\partial p_s(x, y)}{\partial s} \right|
    \end{align}
    for some $s$ between $\epsilon^2 + t + \tau(t)$ and $\epsilon^2 + t$.
   Since 
    \begin{align*}
        \partial_ s p_s(x, y)
        &=
        \partial_s
        \left(
            \frac{1}{(2 \pi s)^{d/2}}
            \exp\left( - \frac{\|x - y\|^2}{2 s} \right)
        \right)
        \\ &=
        - \frac{d}{2s} p_s(x, y) + \frac{\|x - y\|^2}{2 s^2} p_s(x, y),
    \end{align*}
    applying the inequality~\eqref{eqn:p_deriv_term2},
    using the fact that $p_s(x, y) \le 2^{d/2} p_{2s}(x,y)$,
    and then \eqref{eqn:p_bounded_on_interval},
    we have that for any $s \in ((\epsilon^2 + t)/ 2, 3(\epsilon^2 + t))$,
    \begin{align*}
        \left| \frac{\partial}{\partial s} p_s(x, y) \right|
        \le
        \frac{C}{s} p_{2s}(x, y) 
        \le
        \frac{C}{\epsilon^2 + t} p_{6(\epsilon^2 + t)}(x, y) .
    \end{align*}
    Therefore, recalling that $\IE[\tau(t)^2] = t / \theta$, substituting 
into~(\ref{deduction from IVT}),
    \begin{align*}
        \IE\left[
            1_{A_3}
            \left|
                p_{\epsilon^2 + t + \tau(t)}(x, y)
                -
                p_{\epsilon^2 + t}(x, y)
            \right|
        \right]
        &\le
            \frac{C}{\epsilon^2 + t}
                p_{6(\epsilon^2 + t)}(x, y)
            \IE\left[|\tau(t)|\right]
        \\ &\le
            \frac{C}{\epsilon^2 + t}
                p_{6(\epsilon^2 + t)}(x, y)
            \IE\left[\tau(t)^2\right]^{1/2}
        \\ &=
            \left( \frac{Ct}{\theta(\epsilon^2 + t)^2} \right)^{1/2}
                p_{6(\epsilon^2 + t)}(x, y)
        \\ &\le
            \frac{C}{\sqrt{\theta \epsilon^2}}
                p_{6(\epsilon^2 + t)}(x, y) ,
    \end{align*}
    where the last inequality follows from $2 \epsilon^2 t \le (\epsilon^2 + t)^2$.

@@

    Expanding the difference of two squares,
    \begin{align*}
        e^{- \frac{\|y-z\|^2}{2 s}}
        -
        e^{- \frac{\|x-z\|^2}{2 s}}
        &=
        \left(
            e^{-\frac{\|y-z\|^2}{4 s}}
            -
            e^{-\frac{\|x-z\|^2}{4 s}}
        \right)
        \left(
            e^{-\frac{\|y-z\|^2}{4 s}}
            +
            e^{-\frac{\|x-z\|^2}{4 s}}
        \right) .
    \end{align*}
Now, thinking of the first term in brackets as a function of a single variable $x$ on
the line segment $[y,z]$ connecting $y$ to $z$, we can apply the
Intermediate Value Theorem and take the modulus to bound this expression by 
    \[
        \|y-x\|
        \left( \frac{2\|w-z\|}{4s} \exp\left(-\frac{\|w-z\|^2}{4s}\right)\right)
        (4 \pi s)^{d/2}
        \left( p_{2s}(y,z)+p_{2s}(x,z) \right)
    \]
    for some $w\in [y,z]$.
    Using the fact that $x e^{-x^2}$ is uniformly bounded,
    we can bound the first bracket in the last equation by $C/\sqrt{s}$, and the result follows.
\end{proof}

@@

\big\langle (p_{s-r+\epsilon^2}(y,z)-p_{s-r+\epsilon^2}(w,z)|)

@@

	+ \big\langle\frac{C}{(\theta\epsilon^2)^{1/2}} \Big(
	p_{6(\epsilon^2+s)}(y,z)+p_{6(\epsilon^2+s)}(w,z)\Big)
	+\widehat{\epsilon}(\delta,\epsilon,\theta)

@@

    \big(p_{2(s+\epsilon^2)}(y,z)+p_{2(s+\epsilon^2)}(w,z)\big),\eta_0(dz)\Big\rangle

@@

    \big(p_{2(s-t+\epsilon^2)}(y,z)+p_{2(s-r+\epsilon^2)}(w,z)\big)

@@

(p_{6(s-r+\epsilon^2)}(y,z)+ p_{6(s-r+\epsilon^2)}(w,z))
+\widehat{\epsilon}(\delta,\epsilon,\theta)\Big\}

@@

We now turn to the identification of the limit points of the sequence 
$\big\{\big(\rho_\epsilon*\eta_t^N(x)dx\big)_{t\geq 0}\big\}_{N\geq 1}$.
We would like to show that any limit point solves~\eqref{target equation in local convergence}
in the limit, i.e.,
\begin{equation}\label{eqn:target PDE weak form}
    \langle f(x), \varphi(t,x)dx \rangle
    =
    \int_0^t
        \Big\langle
        \frac{1}{2}\Delta f(x) + f(x) F(\varphi(s,x))
        ,
        \varphi(s,x) dx
        \Big\rangle
    ds .
\end{equation}
Since 
$\langle f, \rho_\epsilon*\eta_t^N(x)dx\rangle=
\langle \rho_\epsilon*f(x), \eta_t^N(dx)\rangle$,
and the limit is deterministic,
this will follow if we can show that each the terms in the semimartingale
decomposition~(\ref{eqn:eta_martingale}),
with the test function $f$ replaced by $\rho_\epsilon*f(\cdot)$,
converges to the corresponding term in~\eqref{eqn:target PDE weak form}.

The linear term is straightforward.
Write $T_{\cdot}$ for the heat semigroup, so that
$\rho_\epsilon*f(x) = T_{\epsilon^2}f(x)$.
By a Taylor expansion,
\begin{align*}
\int_0^t \big\langle \mathcal{L}^\theta T_{\epsilon^2} f, 
	\eta_s^N(dx)\big\rangle ds 
&= \int_0^t \big\langle \frac{1}{2} \Delta T_{\epsilon^2} f(x), 
	\eta_s^N(dx) \big\rangle 
	+ \mathcal{O}\Big(\frac{1}{\theta}\Big) 
\\ &= \int_0^t \big\langle \frac{1}{2} \Delta f(x), \rho_\epsilon* \eta_s^N(x) dx 
	\big\rangle ds + \mathcal{O}\Big(\frac{1}{\theta}\Big).
\end{align*}
Thus, from weak convergence we can deduce that under our scaling,
for any (weakly) convergent subsequence $\{\rho_\epsilon*\eta^N(x)dx\}_{N\geq 1}$,
\[ 
\int_0^t \big\langle \mathcal{L}^\theta T_{\epsilon^2} f, 
\eta_s^N(dx)\big\rangle ds 
\rightarrow \int_0^t \big\langle \frac{1}{2} \Delta f(x), 
\varphi (s,x) dx \big\rangle ds. 
\]

@@

We first note that,
\begin{align*}
    &
\langle T_{\epsilon^2} f(y) F(\rho_\epsilon * \eta_s(y)), 
\rho_\epsilon * \eta_s(y) dy \rangle 
-\langle T_{\epsilon^2} f(y) F(\rho_\epsilon *\eta_s(dy)), \eta_s(dy) \rangle 
\\ 
& = 
\langle \int T_{\epsilon^2} f(y) 
F(\rho_\epsilon * \eta_s(y))\rho_\epsilon(y-w) dy, \eta_s(dw)\rangle - \langle 
T_{\epsilon^2} f(w) F(\rho_\epsilon*\eta_s(w)), \eta_s(dw) \rangle 
\\ 
&= 
\langle \int \big\{ T_{\epsilon^2} f(y) F(\rho_\epsilon*\eta_s(y))-T_{\epsilon^2}f(w) 
F(\rho_\epsilon*\eta_s(w))\big\} 
\rho_\epsilon(w-y)dy, \eta_s(dw) \rangle.
\end{align*}
Let us denote the integral against $dy$ in the last expression by $I$, that is 
\[ I :=  \int \{ T_{\epsilon^2} f(y) 
F(\rho_\epsilon*\eta_s(y))-T_{\epsilon^2}f(w) 
F(\rho_\epsilon*\eta_s(w))\} \rho_\epsilon(w-y)dy, \]
and note that $|I|$ is bounded by
\begin{align}
& \int 
\Big\{ |F(\rho_\epsilon*\eta_s(y))-F(\rho_\epsilon*\eta_s(w))|T_{\epsilon^2}f(y)+
F(\rho_\epsilon*\eta_s(w))|T_{\epsilon^2}f(y)-T_{\epsilon^2}f(w))|\Big\} 
\rho_{\epsilon}(w-y)dy
\nonumber \\ &\leq \int \| f\|_{\infty} 
\big|F(\rho_\epsilon*\eta_s(y))-F(\rho_\epsilon*\eta_s(w))\big| \rho_\epsilon(w-y)dy + 
C \epsilon\|f' \|_\infty |F(\rho_\epsilon*\eta_s(w))|, \label{FirstBoundCT}
\end{align}
where we have used that 
\[
\int |T_{\epsilon^2}f(y)-T_{\epsilon^2}f(w)| p_{\epsilon^2}(w,y)dy
\leq \|f'\|_\infty\int|y-w|p_{\epsilon^2}(w,y)dy.
\]
Now recall that $F$ is a polynomial of degree $n$, and so 
there exist real numbers $b_k$ such
that $F(a)-F(b)= (a-b)\sum_{k=1}^{n-1} b_k a^k b^{n-1-k}$ and so 
\[
|F(\rho_\epsilon*\eta_s(y))-F(\rho_\epsilon*\eta_s(w))|
\leq 
|\rho_\epsilon*\eta_s(y)-\rho_\epsilon*\eta_s(w)|
\sum_{k=1}^{n-1}|b_k|\left(\rho_\epsilon*\eta_s(y)^{n-1}+\rho_\epsilon*\eta_s(w)^{n-1}\right).
\]

Combining the above, we have reduced the problem to showing that for any $k \ge 0$,
\begin{equation}
\label{target expression}
	\lim_{\epsilon\to 0}
	\IE\Big[	\int_0^t\big\langle \int |\rho_\epsilon*\eta_s(y)-\rho_\epsilon*\eta_s(w)|
\left(\rho_\epsilon*\eta_s(y))^k+\rho_\epsilon*\eta_s(w)^k\right)
	p_{\epsilon^2}(w,y)dy, \eta_s(dw)\big\rangle ds\Big]
=0 .
\end{equation}
We are going to use the estimate~(\ref{difference in rhos}).
First note that by Lemma~\ref{bounds on moments}
the contribution to~(\ref{target expression}) from the integral over
the time interval $[0,\delta]$ is ${\mathcal O}(\delta)$. We focus instead
on the interval $(\delta, t]$.
